An Airdrop That Preserves Recipient Privacy

### 2019-01-10 paper/paper.tex
move 'warm-up' ECDSA airdrop before RSA airdrop
also: break into separate file
translate notes into skeleton of ECDSA section

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Private airdrop: definitions}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{A private airdrop to ECDSA and Schnorr public keys}

TODO: needs to be written.  Maybe put this first because it is so much
simpler?

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{A private airdrop to RSA public keys}

@@

\subsection{Proving knowledge of the factorization of a hidden integer}

@@

\subsection{The concrete airdrop system}

>>>>

\rsw{stashed note from talk with DB}
Simultaneously using the schemes of \S\ref{sec:dsa} and \S\ref{sec:rsa}
    on the same blockchain allows distinguishing between users based on
    key type.
Can work around this using generic ZKPK, at substantial performance cost.
(Alt narrative: talk about generic ZKPK first, then specialize to get better
    perf. at cost of distinguishing.)

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Private airdrop: definitions}\label{sec:defs}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\input{pad_ecdsa.tex}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{A private airdrop to RSA public keys}\label{sec:rsa}

@@

\subsection{Proving knowledge of the factorization of a hidden integer}\label{sec:rsa:proving}

@@

\subsection{The concrete airdrop system}\label{sec:rsa:airdrop}
